Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-03-15 manuscript.Rmd
started writing discussion

---
title             : "Full-day, in home validation of infant body position measurements from inertial sensors"
shorttitle        : "Infant position in the home"

@@

### How Well did Recordings Capture Infants' Entire Day?

@@

@@

Nice to have video to confirm. Best practice in LENA is to still do some transcription yourself to see what cases it works. Still helpful to have other sources to triangulate against.

@@

## Limitations
- No validation at the end of the day (practically this would be hard to do, syncing a challenge)
- Limited to within the home. Driving/strollers are motion signals we don't have training data for, but this could be added in the future. 
- Relying on CG reports of naps/diaper changes.

>>>>

---
title             : "Long-form recording of infant body position in the home using wearable inertial sensors"
shorttitle        : "Infant position in the home"

@@

### How Well Did Recordings Capture Infants' Entire Day?

@@

Across three analyses, we demonstrated the validity of long-form recordings of infant body position using wearable inertial sensors. Both group and individual models trained during the proximal comparison period performed well on testing data collected from the same recording period. Most important, accuracy was consistently strong later in the recording when behavior was completely unsupervised: Human-coded and model-predicted durations of body positions during the distal comparison period were highly correlated, even when narrowing to the scale of 10 minutes. Examining full recordings showed that the new method allows us to capture more data (median = `r apa_num(median(coverage$hours_recorded))` hours of awake behavior) than is typical with video methods (1-2 hours) while simultaneously reducing the human labor needed to annotate it. Ultimately, age differences in body position mirrored past findings that employed other methods, suggesting that the end product is suitable for describing developmental changes in motor behavior.

@@

Nice to have video to confirm. Best practice in LENA is to still do some transcription yourself to see what cases it works. Still helpful to have other sources to triangulate against. Maybe don't use it for a holding detector.

@@

## Limitations
- No validation at the end of the day (practically this would be hard to do, syncing a challenge)
- Limited to within the home. Driving/strollers are motion signals we don't have training data for, but this could be added in the future. 
- Relying on CG reports of naps/diaper changes. 
- Bias in training data
